Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-15 writeup/rocha_etal.tex
Adds figure 4

\begin{figure*}[ht]
\begin{center}
\hspace{-1.25cm}\includegraphics[width=.75\textwidth]{figs/fig1_1.pdf}\\
\vspace{-.125cm}
\includegraphics[width=.75\textwidth]{figs/fig1_2.pdf}
 \caption{(a) The study region with the subregion where the LLC outputs are
          analyzed. Colors represent the topography and white lines are contours of absolute
          dynamic topography every 0.1 m from AVISO. LLC 4320 (1/48$^\circ$) snapshots of surface vorticity (b and c) and transects
          of potential density at 165$^\circ$E (d and e). The snapshots were
          taken at 00:00 UTC.}
\vspace{-1.5cm}
 \label{fig1}
 \end{center}
 \end{figure*}

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=1.\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) kinetic energy (a) and sea-surface height variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, and dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}

Figure \ref{fig4}a depicts the horizontal wavenumber spectra of surface KE in
April and October. At scales larger than 20 km, the April and October spectra based on hourly
velocity snapshots (solid lines) are nearly indistinguishable from each other within 95$\%$ confidence level.
Consistent with the results of
\citet{rocha_etal2016}, who analyzed a 3-month output of the LLC4320 simulation in Drake Passage,
there is significant high-frequency variabilty at submesoscales. Daily-averaging
the velocity field suppresses spatial variability at scales smaller than about 250
km, both in April and October (compare solid lines against dashed lines in Figure
\ref{fig4}a). But this suppression is dramatic in October, when the inertia-gravity waves peak. At scales
smaller than 100 km, 39$\%$ of the surface KE in April is accounted for by super-inertial
flows as opposed to 79$\%$ in October. The seasonality of subinertial submesoscale flows
is strong, consistent
with the results of \citet{sasaki_etal2014}, which are
based on daily-averaged velocity fields of a different model without tidal forcing
(P. Klein, personal communication).

The inertia-gravity waves project on the sea-surface.
There is a dramatic difference between the spectra
based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig4}b): at scales smaller than 100 km, the spectra
of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface submesoscale inertia-gravity waves conspire to yield weak seasonality
in the spectra of KE and sea-surface height variance based on hourly fields.

@@

% \section{Projection on time scales}
% To better understand the high-frequency/high-wavenumber flows  we calculate frequency
% spectra of surface KE winter \ref{fig4}). To obtain statistically meaningful results,
% we average spectral estimates along a section at 165$^\circ$E.  There is about 50
% independent spectral realizations.
%
% The surface KE spectra of subinertial flows very roughly follow a $-2$ power-law.
% The high-frequency flows are split near-inertial flows, tidal signals and their
% higher harmonics. Hence these high-frequency flows are dominated by inertia-gravity
% waves. (Note that the inertial peak nearly merges with the
% diurnal tide peak.) There is statistically significant seasonality. The seasonal
% cycle of the sub-inertial motions (at least for periods between 5-20 days)
% is out-of-phase with the seasonal cycle of supra-inertial flows: the former flows
% are more energetic in April and the latter in October.
%
% Most of these high-frequency inertia-gravity waves project onto scales smaller
% than 100 km. The surface KE spectra of 100-km-smoothed velocity field is significantly
% suppressed in supra-inertial frequencies --- there are no statistically significant
% changes at sub-inertial frequencies (see dashed lines in figure \ref{fig4}).

>>>>

\begin{figure*}[ht]
\begin{center}
\hspace{-1.25cm}\includegraphics[width=.75\textwidth]{figs/fig1_1.pdf}\\
\vspace{-.125cm}
\includegraphics[width=.75\textwidth]{figs/fig1_2.pdf}
 \caption{(a) The study region with the subregion where the LLC outputs are
          analyzed. Colors represent the topography and white lines are contours of absolute
          dynamic topography every 0.1 m from AVISO. LLC 4320 (1/48$^\circ$) snapshots of
          transects
          of potential density at 165$^\circ$E (b and c) and  surface vorticity (d and e) . The snapshots were
          taken at 00:00 UTC.}
\vspace{-1.5cm}
 \label{fig1}
 \end{center}
 \end{figure*}

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig4.pdf}
 \caption{LLC4320 Wavenumber-frequency spectrum of SSH variance in (a) April and (b) October.
          (c) The ratio between (b) and (a) --- the ratio is masked in regions
          with SSH variance density smaller than $10^{-2}$ m$^2$/[cpkm $\times$ cph].
          The light gray shaded region depicts the dispersion relations for inertia-gravity
          waves from mode 1 through mode 4 across the latitudinal domain; horizontal dashed lines represent the semi-diurnal
          lunar tidal frequency (M$_2$), and the inertial frequency at mid-latitude
          (f$_{32.5}$) and its first harmonic (2f$_{32.5}$).}
 \label{fig4}
 \end{center}
\end{figure*}

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.85\textwidth]{figs/fig5.pdf}
 \caption{Surface (horizontal) kinetic energy (a) and sea-surface height variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, and dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig5}
 \end{center}
\end{figure*}

Figure \ref{fig5}a depicts the horizontal wavenumber spectra of surface KE in
April and October. At scales larger than 20 km, the April and October spectra based on hourly
velocity snapshots (solid lines) are nearly indistinguishable from each other within 95$\%$ confidence level.
Consistent with the results of
\citet{rocha_etal2016}, who analyzed a 3-month output of the LLC4320 simulation in Drake Passage,
there is significant high-frequency variabilty at submesoscales. Daily-averaging
the velocity field suppresses spatial variability at scales smaller than about 250
km, both in April and October (compare solid lines against dashed lines in Figure
\ref{fig5}a). But this suppression is dramatic in October, when the inertia-gravity waves peak. At scales
smaller than 100 km, 39$\%$ of the surface KE in April is accounted for by super-inertial
flows as opposed to 79$\%$ in October. The seasonality of subinertial submesoscale flows
is strong, consistent
with the results of \citet{sasaki_etal2014}, which are
based on daily-averaged velocity fields of a different model without tidal forcing
(P. Klein, personal communication).

The inertia-gravity waves project on the sea-surface.
There is a dramatic difference between the spectra
based on hourly and daily-averaged sea-surface height in October (Figure \ref{fig5}b): at scales smaller than 100 km, the spectra
of hourly sea-surface height roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
sea-surface height roughly follows a $-5$ power-law. At these scales, 33$\%$ of the sea-surface height variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October. Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface submesoscale inertia-gravity waves conspire to yield weak seasonality
in the spectra of KE and sea-surface height variance based on hourly fields.

@@

% \section{Projection on time scales}
% To better understand the high-frequency/high-wavenumber flows  we calculate frequency
% spectra of surface KE winter \ref{fig5}). To obtain statistically meaningful results,
% we average spectral estimates along a section at 165$^\circ$E.  There is about 50
% independent spectral realizations.
%
% The surface KE spectra of subinertial flows very roughly follow a $-2$ power-law.
% The high-frequency flows are split near-inertial flows, tidal signals and their
% higher harmonics. Hence these high-frequency flows are dominated by inertia-gravity
% waves. (Note that the inertial peak nearly merges with the
% diurnal tide peak.) There is statistically significant seasonality. The seasonal
% cycle of the sub-inertial motions (at least for periods between 5-20 days)
% is out-of-phase with the seasonal cycle of supra-inertial flows: the former flows
% are more energetic in April and the latter in October.
%
% Most of these high-frequency inertia-gravity waves project onto scales smaller
% than 100 km. The surface KE spectra of 100-km-smoothed velocity field is significantly
% suppressed in supra-inertial frequencies --- there are no statistically significant
% changes at sub-inertial frequencies (see dashed lines in figure \ref{fig5}).
